The Driving Forces of API Evolution

### 2015-06-03 thesis/paper.tex
validity

\smallskip \noindent
\textbf{Construct validity  } Since our study is largely based on existing theories \cite{chapin2001types, lehman90sview}, the validity of it directly correlates to the validity of the theories and the applicability of them.

@@

\smallskip \noindent
\textbf{External validity  } The results of our study should be highly generalisable to similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors. Our study can especially be compared to similar studies conducted on platform or embedded APIs. Further comparability to our study is offered through how the results are structured around established software evolution theories.

>>>>

\smallskip \noindent
\textbf{Construct validity  } Since our study is largely based on existing theories \cite{chapin2001types, lehman90sview}, the validity of it directly correlates to the validity of the theories and the applicability of them. With regards to Lehman's laws of software evolution, the laws are said to only apply to E-type systems. According to our analysis, we consider the API to be of the E-type, but our interpretations of Lehman's definitions are incorrect, it could be considered a threat to the construct of our study.

@@

\smallskip \noindent
\textbf{External validity  } Since only two versions of the API were analysed, we cannot claim any generalisability for our study. We do, however, believe that our study can offer comparability for companies that chose to do a similar analysis on their API.
